Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance

### 2019-06-05 Manuscript/manuscript.Rmd
results edits

## MODEL CONSTRUCTION

To establish the data for modeling, the genome was binned into equally sized intervals defined by the data resolution of the corresponding contact matrix. As an example, for domain data obtained from a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals. In order to accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix. That is, for 10 kb resolution data, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb. A genomic bin was then labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary. Otherwise, the bin was labeled as not containing a boundary (Y=0).

@@

## CELL LINE AND DATA [??? What data?] RESOLUTION SPECIFIC MODEL [??? What model?] CONSTRUCTION [??? Why?]

We analyzed [??? Boring. What problem you are solving?] publically available Hi-C data for the GM12878 and K562 cell lines provided by Rao et al. [@rao20143d]. Topologically associating domains were identified using the Arrowhead algorithm [@durand2016juicebox] obtained at 10 kb, 25 kb, 50 kb, and 100 kb resolutions. We then established a unified approach toward preparing cell line and resolution specific TAD boundary data [??? This is problem definition, should be done early on, not here] for predictive modelling purposes. Specifically, we created a response variable that indicated whether a genomic bin overlapped with a flanked TAD boundary ($Y=1$), or not ($Y=0$) (Figure 1). <!--The unit width of each bin on the linear genome corresponded to the resolution of the cell line specific contact matrix on which domains were called. Moreover, TAD boundaries were flanked on either side by the same unit length as the genomic bins to account for uncertainty in boundary location.-->

>>>>

## CLASSIFICATION

To establish the data for classification, the genome was binned into equally sized intervals defined by the data resolution of the corresponding contact matrix. As an example, for domain data obtained from a 10 kb resolution contact matrix, the genome was binned into 10 kb intervals. In order to accommodate for the uncertainty in exact boundary location, the boundary points were flanked on both sides by the size of the resolution of the corresponding contact matrix. That is, for 10 kb resolution data, each uniquely identified TAD boundary was flanked on either side by 10 kilobases for a total width around each boundary point of 20 kb. A genomic bin was then labeled as having a TAD boundary within it (Y=1) if it overlapped with a particular flanked boundary. Otherwise, the bin was labeled as not containing a boundary (Y=0).

@@

## Data construction for unbiased comparisons between resolution specific random forest classifiers
<!--## CELL LINE AND DATA [??? What data?] RESOLUTION SPECIFIC MODEL [??? What model?] CONSTRUCTION [??? Why?] !!!created new header-->

In total, we analyzed publically available Hi-C data for both the GM12878 and K562 cell lines, at four resolutions including 10 kb, 25 kb, 50 kb, and 100 kb. Given the varying levels of data resolution, we created a resolution-specific approach toward data constuction used for downstream modelling (Figure 1). This allowed us an unbiased way to compare performances of random forest classifiers between varying resolutions of Hi-C data. [??? Boring. What problem you are solving?;!!!editted]
